A First Effort for a Distributed Segment-based Approach on Self-Assembled Nano Networks

### 2013-09-20 trunk/PAPER/disr.tex
Removed some contracted verbal forms, and typos

\subsection{Basic Idea}
The main concept behind of the original SR approach is the
\emph{Segment}: a Segment is basically a path of consecutive node
and links. All segments start with a link attached to a node which
belongs to different segment, ending with a link also attached to a
node belonging to a different segment. A exception is the first
segment estabilished in the network, called \emph{starting segment} which it's  a loop
beginning/ending on a particular node defined as boostrap node.

@@

% TODO: the following it's true, but complicates things at this stage
%Note that a value different from \emph{NULL} does not
%necessarily mean the node has been assigned to some segment (e.g. when
%searching starting segment is set \emph{visited} by default even if not yet
%assigned to any segment).

\item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
being considered as candidate for a segment, and the \emph{segID} value
specifies the segment id for which the node it's candidate. 
\item{\emph{link\_visited[]}}: an array
of values representing information about attached links, that is, the
segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
assigned.
%TDB: do we need to introduce some value for the
%“bridge” status ? (e.g. a node connecting the terminal node of a
%subnet with the starting one of another) 
\item{\emph{link\_tvisited[]}}: an array of
values representing information about attached links, that is, the \emph{segID} of
the segment for which the link is candidate. When \texttt{NULL}, the link is
currently not \emph{tvisited}.  
\end{itemize}
%\item{\emph{starting}}: boolean, \emph{true} if the node it's a
%starting node from which the whole process was initiated.
%\end{itemize}

@@

\begin{itemize}
\item{\emph{Free}}: a node that has  not been yet considered  by the DiSR algorithm.
The node is not marked as \emph{visited}/\emph{tvisited}.
\item{\emph{Boostrap}}: a node which has been explicitly set as bootstrap node from
an upper layer via. 
% TODO: this and all the other details on the items below should be
% checked and moved elsewhere for a future long paper

@@

\begin{itemize}
\item The node it's not candidate or assigned: it should set itself as
\emph{Candidate} and forward the packet along its free links, using
flooding.  
\item The node is \emph{Candidate} with the same
\emph{segID} and \emph{src\_id} is equal to node id: this means the
node was the initiator of the request, so a starting segment was found and
should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{Candidate}, with the same \emph{segID} of the
packet but \emph{src\_id} is different from node id: due
the flooding mechanism, another starting segment packet reached a node
which was previously marked as \emph{Candidate} from the same starting segment
search process. Since the node is candidate with the same id, it means
that it already accomplished in the task of propagating that kind
packets, thus can simply ignore the event thrashing the packet.  
%TBD: how the status should be changed ? depend on the flooding mechanism. Note
%that these links don’t include the link from which the request was
%received.  
\item The node is \emph{Candidate}, with a different \emph{segID}: 
this simply means that the starting segment received it's deprecated,
because the node has already accepted non-starting segment requests
originated from other \item{Assigned} nodes.
\item The node it's \emph{Assigned}, with a different \emph{segID}:
same as the previous case.

% TODO: check and remove, the below it's not true
%CHECK:  it is not the initiator of the starting segment request, but
%is already assigned to some segment!? assuming again we are discussing
%of nodes belonging to the same subnet, this should NOT happen, since
%the only visited node of the subnet should be the initial node from
%which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
%assuming that if the the node is visited or \emph{tvisited} with the id of
%another subnet can simply ignore the request.  The node it's \emph{tvisited}
%but it's not the initiator of the request (different id): same as
%above, if we are assuming nodes of the same subnet, this shouldn’t
%happen. If the node is of another subnet, can simply ignore the event.

@@

\begin{itemize}
\item The node is \emph{Assigned}: a segment was
found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{Candidate}: it should discard the packet sending
back a \texttt{SEGMENT\_CANCEL} 
\item The node it's not \emph{Assigned} or \emph{Candidate} and has free
links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
to one of its free links, according to some internal ordering
\end{itemize}

NOTE: the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
itself it's included in the segment , while in the second case the
receiving node does not belong to the segment found.

@@

\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
the packet, the node learns to belong to the segment associated to the
id. Further, it should forward this packet to the link where the
original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
can learn the segment id they belong to.  \emph{LED} shoud be
updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
\emph{link\_visited} variable associated to the incoming confirm should be set
as segID. Note that if the request was flooded across different links,
the \emph{link\_visited} variable associated to the other paths shouldn’t be
set.  the \emph{link\_visited} variable associated to the link from which the
request was originated should be set segID

>>>>

\subsection{Basic Idea}
The main concept behind of the original SR approach is the
\emph{Segment}: a Segment is basically a path of consecutive node
and links. All segments start with a link attached to a node which
belongs to different segment, ending with a link also attached to a
node belonging to a different segment. A exception is the first
segment estabilished in the network, called \emph{starting segment} which is  a loop
beginning/ending on a particular node defined as bootstrap node.

@@

% TODO: the following is true, but complicates things at this stage
%Note that a value different from \emph{NULL} does not
%necessarily mean the node has been assigned to some segment (e.g. when
%searching starting segment is set \emph{visited} by default even if not yet
%assigned to any segment).

\item{\emph{tvisited}}: a boolean value. If \emph{true}, the node is
being considered as candidate for a segment, and the \emph{segID} value
specifies the segment id for which the node is candidate. 
\item{\emph{link\_visited[]}}: an array
of values representing information about attached links, that is, the
segID of the segment owning each link. When \texttt{NULL}, the corresponding link has not yet been
assigned.
%TDB: do we need to introduce some value for the
%“bridge” status ? (e.g. a node connecting the terminal node of a
%subnet with the starting one of another) 
\item{\emph{link\_tvisited[]}}: an array of
values representing information about attached links, that is, the \emph{segID} of
the segment for which the link is candidate. When \texttt{NULL}, the link is
currently not \emph{tvisited}.  
\end{itemize}
%\item{\emph{starting}}: boolean, \emph{true} if the node is a
%starting node from which the whole process was initiated.
%\end{itemize}

@@

\begin{itemize}
\item{\emph{Free}}: a node that has  not been yet considered  by the DiSR algorithm.
The node is not marked as \emph{visited}/\emph{tvisited}.
\item{\emph{Bootstrap}}: a node which has been explicitly set as bootstrap node from
an upper layer via. 
% TODO: this and all the other details on the items below should be
% checked and moved elsewhere for a future long paper

@@

\begin{itemize}
\item The node is not candidate or assigned: it should set itself as
\emph{Candidate} and forward the packet along its free links, using
flooding.  
\item The node is \emph{Candidate} with the same
\emph{segID} and \emph{src\_id} is equal to node id: this means the
node was the initiator of the request, so a starting segment was found and
should be confirmed sending back a \texttt{STARTING\_SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{Candidate}, with the same \emph{segID} of the
packet but \emph{src\_id} is different from node id: due
the flooding mechanism, another starting segment packet reached a node
which was previously marked as \emph{Candidate} from the same starting segment
search process. Since the node is candidate with the same id, it means
that it already accomplished in the task of propagating that kind
packets, thus can simply ignore the event thrashing the packet.  
%TBD: how the status should be changed ? depend on the flooding mechanism. Note
%that these links do not include the link from which the request was
%received.  
\item The node is \emph{Candidate}, with a different \emph{segID}: 
this simply means that the starting segment received is deprecated,
because the node has already accepted non-starting segment requests
originated from other \emph{Assigned} nodes.
\item The node is \emph{Assigned}, with a different \emph{segID}:
same as the previous case.

% TODO: check and remove, the below is not true
%CHECK:  it is not the initiator of the starting segment request, but
%is already assigned to some segment!? assuming again we are discussing
%of nodes belonging to the same subnet, this should NOT happen, since
%the only visited node of the subnet should be the initial node from
%which the \texttt{STARTING\_SEGMENT\_REQUEST} originated. Note again that we are
%assuming that if the the node is visited or \emph{tvisited} with the id of
%another subnet can simply ignore the request.  The node is \emph{tvisited}
%but it is not the initiator of the request (different id): same as
%above, if we are assuming nodes of the same subnet, this should not
%happen. If the node is of another subnet, can simply ignore the event.

@@

\begin{itemize}
\item The node is \emph{Assigned}: a segment was
found and it should be confirmed sending back a \texttt{SEGMENT\_CONFIRM}
packet.  
\item The node is \emph{Candidate}: it should discard the packet sending
back a \texttt{SEGMENT\_CANCEL} 
\item The node is not \emph{Assigned} or \emph{Candidate} and has free
links: it marks itself as \emph{Candidate} and forwards the \texttt{SEGMENT\_REQUEST}
to one of its free links, according to some internal ordering
\end{itemize}

NOTE: the main difference between confirming a \texttt{STARTING\_SEGMENT\_REQUEST}
and confirming a \texttt{SEGMENT\_REQUEST} is that in the first case the node
itself is included in the segment , while in the second case the
receiving node does not belong to the segment found.

@@

\subsection{Receiving a \texttt{SEGMENT\_CONFIRM}}
When received, if the node status is \emph{Candidate} with a \emph{segID} corresponding to the one indicated in
the packet, the node learns to belong to the segment associated to the
id. Further, it should forward this packet to the link where the
original \texttt{SEGMENT\_REQUEST} packet came from, so that all candidate nodes
can learn the segment id they belong to.  \emph{LED} shoud be
updated: The state of the node changes from \emph{tvisited} to \emph{visited}.  the
\emph{link\_tvisited} previously set with the \emph{segID} should be invalidated the
\emph{link\_visited} variable associated to the incoming confirm should be set
as segID. Note that if the request was flooded across different links,
the \emph{link\_visited} variable associated to the other paths should not be
set.  the \emph{link\_visited} variable associated to the link from which the
request was originated should be set segID
